A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-06-22 src/paper.tex
Section Second Screen usage in iTV finished

\title{A Second Screen Architecture for Capturing Explicit Viewers' Interactions in TV Environments}
\author{Ricardo~Erikson~V.~de~S.~Rosa, 
	Vicente~Ferreira~de~Lucena~Jr.,\IEEEmembership{Member,IEEE,}
	and~Lucas~Carvalho~Cordeiro
	%
\thanks{Ricardo Erikson V. de S. Rosa is with the Graduate Program in Electrical Engineering, Federal University of Minas Gerais, Av. Antônio Carlos 6627, 31270-901, Belo Horizonte, MG, Brazil(e-mail: ricardoerikson@ufmg.br)}%
\thanks{Vicente Ferreira de Lucena Jr. is with the PPGEE, PPGI, and CETELI - Electronics and Information Technology R\&D Center at UFAM, Manaus, Amazonas, Brazil (e-mail: vicente@ufam.edu.br)}%
\thanks{Lucas Carvalho Cordeiro is with the PPGEE-UFAM, and CETELI - Electronics and Information Technology R\&D Center, Manaus, Amazonas, Brazil (e-mail:lucascordeiro@ufam.edu.br)}}

@@

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., changing channels. In explicit interactions, viewers contribute by actively evaluating, commenting or sharing their opinion about a given content. Both kinds of interaction are important for applications that rely on audience generated data.

@@

A review of the related works shown that the usage of personal devices as second screen devices has some advantages. Firstly, the visual elements

@@

>>>>

\title{A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments}
\author{Ricardo~Erikson~V.~de~S.~Rosa, 
	Vicente~Ferreira~de~Lucena~Jr.,\IEEEmembership{Member,IEEE,}
	and~Lucas~Carvalho~Cordeiro
	%
\thanks{Ricardo Erikson V. de S. Rosa is with the Graduate Program in Electrical Engineering, Federal University of Minas Gerais, Av. Antônio Carlos 6627, 31270-901, Belo Horizonte, MG, Brazil(e-mail: ricardoerikson@ufmg.br)}%
\thanks{Vicente Ferreira de Lucena Jr. is with the PPGEE, PPGI, and CETELI - Electronics and Information Technology R\&D Center at UFAM, Manaus, Amazonas, Brazil (e-mail: vicente@ufam.edu.br)}%
\thanks{Lucas Carvalho Cordeiro is with the PPGEE-UFAM, and CETELI - Electronics and Information Technology R\&D Center, Manaus, Amazonas, Brazil (e-mail:lucascordeiro@ufam.edu.br)}}

@@

@@

A review of the related works shown that the usage of personal devices as second screen devices has two main advantages. Firstly, the visual elements (e.g., an EPG guide) that are commonly shown on the TV screen can be presented on the second screen device in such a way that the viewing experience of other viewers is not affected. Secondly, the second screen device can enhance the capabilities of a conventional remote control by providing more sophisticated interactions, e.g., gesture and voice commands.

@@

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., changing channels and adjust sound volume. In explicit interactions, viewers contribute by actively performing actions that are not usual in the their experience from conventional TV. Such actions include among other things, evaluating audio-visual content, commenting and sharing opinion about a given content through iTV applications. Both kinds of interaction are important for services that rely on audience generated data, e.g., content personalization and targeted advertising.
